---
title: "simulation"
output: html_document
author: An-Chiao Liu
---
```{r message=FALSE, warning=FALSE}
library(MASS)
library(ggplot2)
set.seed(13)
nsim <- 100
n <- 300
data <- matrix(data = NA, nrow = nsim, ncol = n)
```

Sample 100 samples from a standard normal distribution.
```{r}
for (i in 1:nsim) {
  
  data[i,] <- mvrnorm(n = n, mu = 0, Sigma = 1)
  
}

data <- as.data.frame(data)
```

absolute bias
standard error
lower bound of the 95% confidence interval
upper bound of the 95% confidence interval
```{r}
Mean <- apply(data, 1, FUN = mean)
Bias <- Mean - 0
SE <- 1/sqrt(n)
Lower <-  Mean - qt(.975, n-1) * SE
Upper <-  Mean + qt(.975, n-1) * SE
```

```{r}
result <- cbind(Mean, Bias, SE, Lower,Upper)
result <- as.data.frame(result)
```

Create a plot that demonstrates the following **“A replication of the procedure that generates a 95% confidence interval that is centered around the sample mean would cover the population value at least 95 out of 100 times”**
```{r}
limits <- aes(ymax = result$Upper, ymin = result$Lower)
ggplot(result, aes(y = Mean, x=1:100)) + 
  geom_hline(aes(yintercept = 0), color = "dark grey", size = 2) + 
  geom_pointrange(limits) + 
  xlab("Simulations 1-100") +
  ylab("Means and 95% Confidence Intervals")
```

Present a table containing all simulated samples for which the resulting confidence interval does not contain the population value.
```{r}
uncover <- result[!(Lower < 0 & 0 < Upper),]
uncover
```

